Making Soup: Preparing and Validating Molecular Simulations of the Bacterial Cytoplasm

### 2019-11-20 paper/rebuttal.txt

Dear Dr. van der Spoel:

Thank you for submitting your manuscript to Journal of Chemical
 Information and Modeling. Please find the enclosed reviews of your
 manuscript. The reviewers have found significant problems with the
 manuscript in its current form, but we are willing to consider a
 revised manuscript in which you have made major revisions and
 responded to the reviewers' concerns. If you resubmit a revised
 manuscript, there may be a second round of external review, perhaps
 including new reviewers.

We would like to receive your revision as soon as possible, by
17-Jan-2020 at the latest.

In addition to addressing the reviewers' comments, please make each of the
technical corrections listed below:

MANUSCRIPT
- Please remove "et al." from your references and list all authors' names.
ANSWER:

- Update the publication information in Reference 56 and Reference 73 when
available.
ANSWER:

- Please include a Table of Contents graphic on the very last page of
your manuscript.  This graphic, in conjunction with the manuscript
title, should give the reader a summary of the research described in
the paper. The Table of Contents graphic will also be published in the
Abstract of the manuscript. This graphic can be no wider than 8 cm and
no taller than 4 cm and should be prepared following the
specifications under Artwork. Text should be limited to essential
technical labels.  More guidance is available at
http://pubs.acs.org/paragonplus/submission/toc_abstract_graphics_guidelines.pdf.
ANSWER:

- The title page of your manuscript file needs more complete
 affiliation information for all authors. Could you please provide
 updated affiliations including all of the following information
 (where possible)? Department and institute (or company name), city,
 state/region, postal code, country.  Please indicate the
 corresponding author's email address with an asterisk.
ANSWER:

- Funding Sources: Authors are required to report ALL funding sources
  and grant/award numbers relevant to this manuscript. Enter all
  sources of funding for ALL authors relevant to this manuscript in
  BOTH the Open Funder Registry tool in ACS Paragon Plus and in the
  manuscript to meet this requirement. See
  http://pubs.acs.org/page/4authors/funder_options.html for complete
  instructions.
ANSWER:

- ORCID: Authors submitting manuscript revisions are required to
  provide their own validated ORCID iDs before completing the
  submission, if an ORCID iD is not already associated with their ACS
  Paragon Plus user profiles. This iD may be provided during original
  manuscript submission or when submitting the manuscript
  revision. You can provide only your own ORCID iD, a unique
  researcher identifier. If your ORCID iD is not already validated and
  associated with your ACS Paragon Plus user profile, you may do so by
  following the ORCID-related links in the Email/Name section of your
  ACS Paragon Plus account. All authors are encouraged to register for
  and associate their own ORCID iDs with their ACS Paragon Plus
  profiles. The ORCID iD will be displayed in the published article
  for any author on a manuscript who has a validated ORCID iD
  associated with ACS Paragon Plus when the manuscript is
  accepted. Learn more at http://www.orcid.org.
ANSWER:

- On resubmission you must submit the following:
a) A point-by-point response to the reviewers.
b) A clean, unmarked copy of the manuscript document file.
c) A marked copy of the revised manuscript in which all the changes are clearly tracked or highlighted. Upload this file as Supporting Information for Review.
d) A clean, unmarked Supporting Information for Publication file, without any highlighting or tracked changes.

- The reviewers indicate that the quality of the written English could
  be improved. Please consider using a native English speaker or an
  English-language editing service to assist with this. The ACS
  maintains a list of editing services:
  https://authoringservices.acs.org/.

JCIM is now accepting images to appear on the front cover of the
journal. If you have a visually arresting and scientifically
interesting image, please email it and a brief (80 word) description
of the image to eic@jcim.acs.org. Additional information about the
technical specifications for the image can be found at
https://pubsapp.acs.org/paragonplus/submission/jcisd8/jcisd8_authguide.pdf.

Please contact the JCIM editorial office at eic@jcim.acs.org if you
have any specific questions regarding these guidelines.

JCIM has a Twitter feed (@JCIM_ACS; https://twitter.com/jcim_acs)
covering the latest news and highlights in the field. If you would
like us to feature your manuscript on this platform, please share a
Tweet of no more than 140 characters. Please feel free to share your
Twitter handle (if you have one) or any other relevant
department/institutional handles. Include this information in the
cover letter of your revised manuscript submission.

ACS Publications uses Crossref Similarity Check Powered by iThenticate
to detect instances of similarity in submitted manuscripts. In
publishing only original research, ACS is committed to deterring
plagiarism, including self-plagiarism. Your manuscript may be screened
for similarity to published material.

Sincerely,

Prof. Rommie Amaro
Associate Editor Journal of Chemical Information and Modeling
Urey Hall 3234, MS - 0340,
La Jolla, CA 92093-0340,
United States
Email : amaro-office@jcim.acs.org

------------------------------------ To revise your manuscript, log
into ACS Paragon Plus with your ACS ID at
http://paragonplus.acs.org/login and select "My Authoring Activity."
Your manuscript will be listed under "Revisions and Resubmissions
Requested by Editorial Office." Click on "Submit Revision" to begin
the submission process. Your manuscript number will be appended to
denote a revision.

When submitting your revised manuscript, you will be able to respond
to the comments made by the reviewer(s) in the text box provided or by
attaching a file containing your response letter.

------------------------------------

Reviewers' Comments to Author:

Reviewer: 1

Comments: Van der Spoel and co-workers built an atomistic model of the
cytoplasm of Escherichia coli composed of 1.5 million atoms and
investigated its behavior based on 3x1 us of molecular dynamics
(MD) simulations. Some interesting observations were made. The most
important aspects of this work are that i) the authors demonstrated
that it has become possible to perform MD simulations of cytoplasms
involving millions of atoms on the microsecond timescale, and ii) they
provide a Python script and a set of files that enable other
researchers to build their own E. coli cytoplasm models.

The work is of highest importance and novelty. Moreover, the
manuscript is nicely written and easy to follow. My recommendation
thus is to accept this manuscript for publication after following
minor comments have been addressed:

ANSWER: Thanks for the encouraging commments.

1) Why did the authors choose K+ and not Na+ to model the ionic
strength of 150 mmol/L? Please comment.

ANSWER: Like most organisms E. coli has a higher concentration of K+
than Na+ of 30-300 mmol/L versus 10 mmol/L Na+. The number 150 is
halfway the interval. A reference to a text book is added.

2) Figure 1A: Even though it is not of importance for the message
conveyed by this figure, this reviewer nonetheless wonders what the
difference between the red and green particles is in that figure. A
short note on it in the caption would be appreciated.

ANSWER: Red is water and green is biomolecules, this has been added to
the caption.

3) p. 13-15: It is mentioned that the RMSD of TufA, MetE and IcdA is
larger in the cytoplasm than in diluted solutions. Based on the RMSF
they also identified which part of these proteins become more
flexible. The authors later speculate that this is due to some
nonspecific interactions. Here, some more analysis is required. The
authors should demonstrate that these changes indeed arise from such
kind of interactions and not more specific interactions. And why are
only certain loops of each protein involved while all other loops seem
almost unaffected. And why does the RMSF of residues 450-460 of MetE
decrease?

ANSWER:

4) Figure 5: Why are the standard errors of the RMSF for CspC so much
larger than for the other systems. Please comment.

ANSWER:

5) In the discussion on p. 17 about the challenge of reproducing
protein-protein interactions one might also cite
DOI:10.1021/acs.jctc.8b00579 where it was shown that current force
fields have problems to distinguish between peptides known from
experiment to aggregate or not to aggregate. Moreover, increasing the
protein-water interactions as done in Amber03-ws may abolish protein
aggregation almost completely.

ANSWER: This paper was cited as well. Nevertheless, our earlier study
(Zhang et al, JCIM 58, 2018, 1037) showed that the DeltaGhydration are
slightly better using Amber99-sbws than Amber03-ws which is why we
used particular combination.

6) Following spelling/grammatical mistakes should be corrected:
p. 8, l. 29: A verb is missing in that sentence.
p. 10, l. 47: Change "don't" to "do not". =20
p. 11, l. 17: Add a space between "500" and "ps".
p. 15, l. 54: Change "of avoid" to "to avoid".
p. 16, l. 50: Change "duffusion" to "diffusion".

ANSWER: All fixed, thanks for finding these.

Reviewer: 2

Comments: Bortot et al. studied protein crowded systems using
molecular simulations with explicit solvent. MD simulations of
macromolecules in crowded conditions help us to understand protein
behaviors in a living cell. Recently, several computational scientists
performed MD simulations of multiple proteins in crowded conditions
and examined the differences of protein structure and dynamics in
crowded condition compared with that in dilute solution. In spite of
the importance of the research field, the paper has three critical
issues. At first, they used only small number of proteins and
tRNA(Phe) in the simulation system, although they call the set up as
the E. coli cytoplasm. Since the proteins can cover only 50 % of the
fraction of E. coli cytoplasm, it is difficult to call the system as
the E. coli cytoplasm. It should be called as a crowded condition that
mimic 50% of volume fraction of the cytosol of E. coli.

ANSWER:

They did not include ribosomes in the system. However, the size
differences between ribosomes and other proteins should be essential
in the cellular crowding effect.

ANSWER:

Secondly, they observed tRNA
aggregation with Mg2+, ATP, and FBP in their systems. They concluded
that completely protonating the phosphate groups of ATP and FBP is
necessary to prevent their aggregation with Mg2+. However, there is no
rationale or experimental evidences on the protonation state of
ATP. Presumably, the Mg2+ model or phosphate model may have
problems. Another possibility is that they used Amber99sb-ws, where
the 1.10 scaling is used for LJ interactions between water and
macromolecules. If they applied the scaling also to tRNA, tRNA
structure could be unfolded. However, there is no data about tRNA
structural changes in crowded condition compared to that in
solution.

ANSWER:

Thirdly, except for the protonation state, there are few novel
biophysical insights in the current work. Essentially same data on
diffusion or RMSD were already shown in the previous crowding papers,
although the length of simulations and the force fields are
different. Although the modeling strategy (Figure 1) seems to be
interesting, the rest of scientific results and discussion may have
rooms for improvements. In particular, the issue of the aggregation of
tRNA in the simulations should be overcome by the refinement of ion
models or the tRNA-water interaction scaling factors.

ANSWER:

### 2019-11-20 paper/virtual_cytoplasm_v2.tex
Some cleanups and documentation
First update to answer referees

\subsection{General simulation setup}
The cytoplasm model was built at a 30\% biomolecular mass fraction and
a physiological salt concentration of 0.15 mol/L KCl. Dropplets containing each component of the model surronded by water and counter-ions were inserted in an empty box in random positions and orientations. Since the volume of this box was initially bigger than what was strictly necessary to accomodate all components, the system was allowed to shrink in a short simulation. Details about how the simulation box was built and optimized are in the results section. All
simulations were performed with the GROMACS 2018
package~\cite{Abraham2015a,Pronk2013a} using the Amber99SB-ws force
field~\cite{Best2014a}, a modified version of the Amber99SB force
field, in combination with the TIP4P/2005 water
model~\cite{Abascal2005b} and improved K$^+$ parameters~\cite{Dang1995a} to avoid the formation of KCl crystals that is observed when using the default parameters of the Amber99SB force field~\cite{Auffinger2007a}. All interactions were calculated explicitly
inside a 1 nm radius and long range electrostatic interactions were
treated using the particle mesh Ewald
algorithm~\cite{Essmann1995a}. Corrections due to long range effects
of dispersion interactions were made to both energy and
pressure~\cite{Allen1987a}. All chemical bonds were constrained at
their equilibrium length using the parallel LINCS
algorithm~\cite{Hess1997a,Hess2008b} allowing an integration time step
of 2 fs. Temperature was kept at 310 K by the v-rescale
thermostat~\cite{Bussi2007a} with a coupling constant of 0.5
ps. Pressure was kept at 1 bar using the Berendsen
barostat~\cite{Berendsen1984a} with the coupling constant of 10.0 ps
during thermalization steps and by the Parrinello-Rahman
barostat~\cite{Parrinello1981a} with the same coupling constant during
production steps.

@@

\subsubsection{RNA fraction}
Transporter RNAs (tRNAs) account for 74\% of the dry weight of
non-ribosomal RNAs~\cite{phillips2012}. Thus, we chose to model the
RNA presence in the cytoplasm with tRNA molecules. Specifically, 
 the tRNA(Phe) molecule as a representative of tRNAs due to
the availability of a recent crystal
structure (4YCO~\cite{Byrne2015}). The protein and RNA content of the total
dry weight of \textit{E.coli} is 55\% and 2.9\%,
respectively~\cite{phillips2012}. That is, the total RNA weight
corresponds to 5\% of the total protein weight. This protein/RNA
weight ratio was used to calculate the correct number of tRNA(Phe)
molecules that were added to the cytoplasm model
\tabref{tbl:soup_components}.

@@

In order to do this, the droplets around each component are also
constructed iteratively. The number of water molecules that we must
place in the simulation box is known from the total biomolecular mass
of the system and the desired biomolecular fraction, which is a
parameter of the model. However, we don't know the thickness of the
water layer around each component, $l$, that accounts for such amount
of water molecules \textit{a priori}. Since $l$ depends on a series of
factors such as the shape, size and abundance of each element, we
define it iteratively. We start by taking a droplet of thickness $l$ =
3 \r{A} around all elements and counting the number of water molecules
that we would add to the box with such droplets. If it is smaller than
the number we need, $l$ is increased by $dl$ = 1 \r{A}. If it is
larger, we reduce the droplet thickness by $dl$, reduce $dl$ by 10
times and then increase $l$ with the new smaller $dl$. We can carry
this process until a user-defined precision cutoff, here 5\%, for the
number of waters in the system is satisfied.

After all droplets are successfully inserted in a simulation box by
the iterative process described above, we proceed to add ions to
neutralize the net charge of the system and to reach the desired ionic
strength. Then, we perform energy minimization and a short simulation
 of 500ps in which all molecules of the box are free to move. In
this step the box shrinks to its optimum size. In our case, the
simulation box shrank from the initial box size of 35 nm to 22.9 nm,
which corresponds to a volume change from 42875 nm\textsuperscript{3}
to 12009 nm\textsuperscript{3}. From this point, the system is ready
to be submitted to the default simulation steps such as thermalization
and production run (please check the materials section for details
about the parameters used).

\begin{figure}[H]
\includegraphics[scale=0.5]{shrinking.pdf} 
\caption{A) The initial simulation box with $L=35.0$ nm and the box
  after the shrinking step, $L=22.9$ nm. B) The evolution of the
  volume of the simulation box during the shrinking simulations. Each
  replica is shown in different colors. }
\end{figure}

@@

The initial detection of aggregation in the cytoplasm model was due to
the outlier behavior of the translational diffusion constant of tRNA
when compared to the other crowders. However, tRNA was not the cause of this
phenomenon. Instead, it was triggered by the exaggerated interactions
between the phosphate-containing metabolites, ATP and FBP, with
Mg$^{2+}$ (Fig.~\ref{fig:avoiding_aggregation}A). tRNA gets involved
in the aggregates because Mg$^{2+}$ is present in the box only as
counter-ion for ATP and tRNA, and so tRNA is one of the few
``sources'' of Mg$^{2+}$ in the whole system. We looked for ways of
avoid aggregation by using simulations of small systems composed of
these metabolites in high concentration, Mg$^{2+}$ and water (please
check the methods section for details).

@@

\section*{Discussion}\label{sec:dissc}
The main difference in behavior of the macromolecules that
compose our model between the crowded system and the dilute condition is
their translational diffusion coefficient, which drops by around
85\% for the proteins and 93\% for the tRNA
(Fig.~\ref{fig:translational_diffusion}A). The slope of the line
generated by fitting a linear regression model to values of
$D_{cyto}/D_{dil}$ is close to zero (slope $= 0.00028$), showing that
the drop in diffusion coefficient is independent of the size of the
macromolecules. We found that the aggregation of ATP$^{3-}$ and
FBP$^{4-}$ around Mg$^{2+}$, which was used as counter-ion for tRNA,
leads to an exaggerated confinement of the tRNA molecules.  Therefore,
tRNA is considered an outlier in the duffusion calculations. In
fact, the slope of the linear regression line fitted to
$D_{cyto}/D_{dil}$ is reduced by by 50\% and  even closer to zero
(slope $= 0.00014$) after removing the diffusion coefficient of tRNA
from the data. These data are in agreement with experimental results
showing that the translational diffusion coefficient of Green
Fluorescent Protein (GFP) in {\em E. coli}, as measured by
fluorescence recovery after photo-bleaching (FRAP), decreased 90\%
when compared to {\em in vitro}
measurements~\cite{Elowitz1999,Konopka2006}.

@@

It has been demonstrated that the force fields that are most widely
used to perform molecular dynamics simulations of macromolecules yield
different results for highly concentrated amino acid
solutions~\cite{andrews2013}. Moreover, it has been reported that
simulations of a highly concentrated environment leads to aggregation
when additive force fields are used~\cite{Petrov2014a,Abriata2015a,
  Nawrocki2017a} and several approaches have been proposed to
eliminate this
problem~\cite{Best2014a,Piana2015a,Bashardanesh2018b}. Apart from
protein-water interactions, the London-dispersion coefficients in the
force fields have been investigated as well but their effect on
protein-protein interactions seems to be
minor~\cite{Mohebifar2017a,Walters2018a,Bashardanesh2018b}.  A
comparison at the amino acid level shows that none of the Amber family
of force fields combined with different water model can simultaneously
produce high accuracy Gibbs energies of hydration and amino acid side
chain mobility~\cite{HZhang2018a}. Of the different combinations
tested in that work the Amber99sb-ws~\cite{Best2014a} in conjunction
with the TIP4P/2005 water model~\cite{Abascal2005b} was deemed the
best compromise~\cite{HZhang2018a}. Nevertheless, in a related paper
we find signs that the increased interaction between protein and water
may be slightly too strong as it leads to partial unfolding of a
protein~\cite{Bashardanesh2019a}.

@@

>>>>

\subsection{General simulation setup}
The cytoplasm model was built at a 30\% biomolecular mass fraction.
Like most organisms E. coli has a higher concentration of K$^+$
(30-300 mmol/L) than Na$^+$ (10 mmol/L)~\cite{Milo2017a}. Therefore a salt
concentration of 150 mmol/L KCl was used.

Dropplets containing each component of the model surronded by water and counter-ions were inserted in an empty box in random positions and orientations. Since the volume of this box was initially bigger than what was strictly necessary to accomodate all components, the system was allowed to shrink in a short simulation. Details about how the simulation box was built and optimized are in the results section. All
simulations were performed with the GROMACS 2018
package~\cite{Abraham2015a,Pronk2013a} using the Amber99SB-ws force
field~\cite{Best2014a}, a modified version of the Amber99SB force
field, in combination with the TIP4P/2005 water
model~\cite{Abascal2005b} and improved K$^+$ parameters~\cite{Dang1995a} to avoid the formation of KCl crystals that is observed when using the default parameters of the Amber99SB force field~\cite{Auffinger2007a}. All interactions were calculated explicitly
inside a 1 nm radius and long range electrostatic interactions were
treated using the particle mesh Ewald
algorithm~\cite{Essmann1995a}. Corrections due to long range effects
of dispersion interactions were made to both energy and
pressure~\cite{Allen1987a}. All chemical bonds were constrained at
their equilibrium length using the parallel LINCS
algorithm~\cite{Hess1997a,Hess2008b} allowing an integration time step
of 2 fs. Temperature was kept at 310 K by the v-rescale
thermostat~\cite{Bussi2007a} with a coupling constant of 0.5
ps. Pressure was kept at 1 bar using the Berendsen
barostat~\cite{Berendsen1984a} with the coupling constant of 10.0 ps
during thermalization steps and by the Parrinello-Rahman
barostat~\cite{Parrinello1981a} with the same coupling constant during
production steps.

@@

\subsubsection{RNA fraction}
Transporter RNAs (tRNAs) account for 74\% of the dry weight of
non-ribosomal RNAs~\cite{phillips2012}. Thus, we chose to model the
RNA presence in the cytoplasm with tRNA molecules. Specifically, 
 the tRNA(Phe) molecule was used as a representative of tRNAs due to
the availability of a recent crystal
structure (4YCO~\cite{Byrne2015}). The protein and RNA content of the total
dry weight of \textit{E.coli} is 55\% and 2.9\%,
respectively~\cite{phillips2012}. That is, the total RNA weight
corresponds to 5\% of the total protein weight. This protein/RNA
weight ratio was used to calculate the correct number of tRNA(Phe)
molecules that were added to the cytoplasm model
\tabref{tbl:soup_components}.

@@

In order to do this, the droplets around each component are also
constructed iteratively. The number of water molecules that we must
place in the simulation box is known from the total biomolecular mass
of the system and the desired biomolecular fraction, which is a
parameter of the model. However, we do not know the thickness of the
water layer around each component, $l$, that accounts for such amount
of water molecules \textit{a priori}. Since $l$ depends on a series of
factors such as the shape, size and abundance of each element, we
define it iteratively. We start by taking a droplet of thickness $l$ =
3 \r{A} around all elements and counting the number of water molecules
that we would add to the box with such droplets. If it is smaller than
the number we need, $l$ is increased by $dl$ = 1 \r{A}. If it is
larger, we reduce the droplet thickness by $dl$, reduce $dl$ by 10
times and then increase $l$ with the new smaller $dl$. We can carry
this process until a user-defined precision cutoff, here 5\%, for the
number of waters in the system is satisfied.

After all droplets are successfully inserted in a simulation box by
the iterative process described above, we proceed to add ions to
neutralize the net charge of the system and to reach the desired ionic
strength. Then, we perform energy minimization and a short simulation
 of 500 ps in which all molecules of the box are free to move. In
this step the box shrinks to its optimum size. In our case, the
simulation box shrank from the initial box size of 35 nm to 22.9 nm,
which corresponds to a volume change from 42875 nm\textsuperscript{3}
to 12009 nm\textsuperscript{3}. From this point, the system is ready
to be submitted to the default simulation steps such as thermalization
and production run (please check the materials section for details
about the parameters used).

\begin{figure}[H]
\includegraphics[scale=0.5]{shrinking.pdf} 
\caption{A) The initial simulation box with $L=35.0$ nm and the box
  after the shrinking step, $L=22.9$ nm. Biomolecules in green, water in red. B) The evolution of the
  volume of the simulation box during the shrinking simulations. Each
  replica is shown in different colors. }
\end{figure}

@@

The initial detection of aggregation in the cytoplasm model was due to
the outlier behavior of the translational diffusion constant of tRNA
when compared to the other crowders. However, tRNA was not the cause of this
phenomenon. Instead, it was triggered by the exaggerated interactions
between the phosphate-containing metabolites, ATP and FBP, with
Mg$^{2+}$ (Fig.~\ref{fig:avoiding_aggregation}A). tRNA gets involved
in the aggregates because Mg$^{2+}$ is present in the box only as
counter-ion for ATP and tRNA, and so tRNA is one of the few
``sources'' of Mg$^{2+}$ in the whole system. We looked for ways to
avoid aggregation by using simulations of small systems composed of
these metabolites in high concentration, Mg$^{2+}$ and water (please
check the methods section for details).

@@

\section*{Discussion}\label{sec:dissc}
The main difference in behavior of the macromolecules that
compose our model between the crowded system and the dilute condition is
their translational diffusion coefficient, which drops by around
85\% for the proteins and 93\% for the tRNA
(Fig.~\ref{fig:translational_diffusion}A). The slope of the line
generated by fitting a linear regression model to values of
$D_{cyto}/D_{dil}$ is close to zero (slope $= 0.00028$), showing that
the drop in diffusion coefficient is independent of the size of the
macromolecules. We found that the aggregation of ATP$^{3-}$ and
FBP$^{4-}$ around Mg$^{2+}$, which was used as counter-ion for tRNA,
leads to an exaggerated confinement of the tRNA molecules.  Therefore,
tRNA is considered an outlier in the diffusion calculations. In
fact, the slope of the linear regression line fitted to
$D_{cyto}/D_{dil}$ is reduced by by 50\% and  even closer to zero
(slope $= 0.00014$) after removing the diffusion coefficient of tRNA
from the data. These data are in agreement with experimental results
showing that the translational diffusion coefficient of Green
Fluorescent Protein (GFP) in {\em E. coli}, as measured by
fluorescence recovery after photo-bleaching (FRAP), decreased 90\%
when compared to {\em in vitro}
measurements~\cite{Elowitz1999,Konopka2006}.

@@

It has been demonstrated that the force fields that are most widely
used to perform molecular dynamics simulations of macromolecules yield
different results for highly concentrated amino acid
solutions~\cite{andrews2013}. Moreover, it has been reported that
simulations of a highly concentrated environment leads to aggregation
when additive force fields are used~\cite{Petrov2014a,Abriata2015a,Nawrocki2017a,Carballo2018a} and several approaches have been proposed to
eliminate this
problem~\cite{Best2014a,Piana2015a,Bashardanesh2018b,Carballo2018a}. Apart from
protein-water interactions, the London-dispersion coefficients in the
force fields have been investigated as well but their effect on
protein-protein interactions seems to be
minor~\cite{Mohebifar2017a,Walters2018a,Bashardanesh2018b}.  A
comparison at the amino acid level shows that none of the Amber family
of force fields combined with different water model can simultaneously
produce high accuracy Gibbs energies of hydration and amino acid side
chain mobility~\cite{HZhang2018a}. Of the different combinations
tested in that work the Amber99sb-ws~\cite{Best2014a} in conjunction
with the TIP4P/2005 water model~\cite{Abascal2005b} was deemed the
best compromise~\cite{HZhang2018a}. Nevertheless, in a related paper
we find signs that the increased interaction between protein and water
may be slightly too strong as it leads to partial unfolding of a
protein~\cite{Bashardanesh2019a}.

@@

\begin{acknowledgement}
The Swedish research council is acknowledged for a grant of computer time
(SNIC2018-2-42) through the High Performance Computing
Center North in Ume{\aa}, Sweden. Funding from eSSENCE - The e-Science
Collaboration (Uppsala-Lund-Ume{\aa}, Sweden) is gratefully acknowledged.
\end{acknowledgement}
